Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming

### 2024-08-01 manuscript_final-2/manuscript_final-2.qmd
HTML 3

![](images/Bee%20Frame%202024-01.jpg){width="674"}

@@

![](images/Bee%20Frame%20Capped%20Honey.jpg){fig-align="center"
width="697"}

@@

![](images/American-Foul-Brood-Comb-1024x768-1.jpg)

@@

![](images/dead-bees-hive-colony-collapse-600nw-2289939105.webp){width="679"}
#Citation section
To cite other work (important everywhere, but likely happens first in
introduction), make sure your references are in the bibtex file
specified in the YAML header above and have the right bibtex key. Then
you can include like this:

@@

![](images/varroa-mite-bee-01.webp){fig-align="center" width="244"}

@@

![](images/Varrpa%201-02.webp){fig-align="center" width="246"}

@@

![](images/Bee%20Feeding-01.jpg){fig-align="center" width="523"}

@@

![](images/_20220406_on_varroadestructor_minden_00463080.jpg){fig-align="center"
width="541"}

@@

#Citations
```{r}
library(knitr)
```

>>>>

![](/images/Bee%20Frame%202024.jpg){fig-align="center"}

@@

![](/images/Bee%20Frame%20Capped%20Honey.jpg){fig-align="center"}

@@

![](/images/American-Foul-Brood-Comb-1024x768-1.jpg){fig-align="center"}

@@

![](/images/dead-bees-hive-colony-collapse-600nw-2289939105.webp)

#Citation section To cite other work (important everywhere, but likely
happens first in introduction), make sure your references are in the
bibtex file specified in the YAML header above and have the right bibtex
key. Then you can include like this:

@@

![](/images/_20220406_on_varroadestructor_minden_00463080.jpg){fig-align="center"}

@@

![](/images/Varrpa%201.webp){fig-align="center" width="527"}

@@

![](/images/Bee%20Feeding.jpg){fig-align="center"}

@@

![](/images/varroa-mite-bee-01.webp){fig-align="center" width="565"}

@@

#Citations
